### 2017-11-07 manuscript.rmd
added commented code for tip-driven node rotation

#Load tree
tree = species_tree_unladder
tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))
tree<-rotateNodes(tree,nodes=c(28,31))
ultratree <- chronos(tree)
class( ultratree ) = "phylo"

>>>>

#Load tree
tree = species_tree_unladder
tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))
tree<-rotateNodes(tree,nodes=c(28,31))
#tree<-rotateNodes(tree,nodes=c(ape::mrca(tree)["Apolemia lanosa", "Agalma elegans"], ape::mrca(tree)["Abylopsis tetragona", "Hippopodius hippopus"]))
ultratree <- chronos(tree)
class( ultratree ) = "phylo"
